One Year HPC Certification Forum in Retrospective

### 2019-04-17 paper.tex
edited the Description of a skill section

Each skill on the tree and even the inner nodes are described in more detail as follows:

\begin{itemize}
  \item \textbf{ID}: ID according the organisation in the skill tree. The last character indicates the level of the skill (Basic, Intermediate, or Advanced).
  \item \textbf{Name}: A speaking name for the skill.
  \item \textbf{Background}: Provides brief information motivating the need for the skill and how this skill fits into the skill tree; what is the bigger picture.
  \item \textbf{Aims}\footnote{The definition of aims and outcomes follows literature for higher education \cite{williamson2011good} and \url{https://www.heacademy.ac.uk/system/files/assessment-learning-outcomes.pdf}.}: They serve as broad purposes and are generally a statement of the intentions of the skill.
  They are not the statements of what a practitioner will learn or do.
  At a basic level, aims are trying to answer two questions: What is the purpose of this skill?
  What is the skill trying to achieve?
  \item \textbf{Learning outcomes (LOs)}: Defines briefly what practitioners will know and learn.
  The objected are statements what prospect learners are able to do, they should
  describe or define an action be clearly stated be measurable/quantifiable to some extent by using action words.
\end{itemize}

On the leaf level, a skill is fine-grained and orthogonal to other skills -- we scope the level of detail here to be able to be taught in a 1.5 hour lecture up to a 4 hour workshop.
We believe this is a good granularity as it allows practitioners to cherry-pick the relevant skills and lecturers and examiners to prepare small lectures with well-defined content.
\ag{change sentence because provided that provide - \\
Instead: For technology-dependent skills on leaf level (e.g., a specific file system or workload manager), often introductory skills are provided that provide the foundation to many specialized skills each representing a specific hardware or software technology.\\
write it this way: For technology-dependent skills on leaf level (e.g., a specific file system or workload manager), often introductory skills are provided that contribute to the foundation of many specialized skills each representing a specific hardware or software technology.
}
The aggregation within the tree is similar to the aggregation found in education as part of “individual teaching events”, “those specified for modules or short courses”, and “those specified for whole degree programmes” \cite{hussey2008learning}.
While that Hussey et al. conclude that LOs on the coarse grained level are not useful for high-level education, we use a similar concept, but relax the granularity/abstraction level of the learning outcome.\kh{den Satz habe ich nicht genau verstanden; als Leser würde ich mir die Kurzbegründung wünschen, die Hussey et al. für ihre Feststellung anführen}

>>>>

Each skill on the tree, including the inner nodes, is described in more detail as follows:

\begin{itemize}
  \item \textbf{ID}: ID according to its position in the skill tree. The last character indicates the level of the skill (Basic, Intermediate, or Advanced).
  \item \textbf{Name}: A name capturing the essence of the skill.  
  \item \textbf{Background}: Provides brief information motivating the need for the skill and how it fits into the bigger picture with other skills. 
  \item \textbf{Aims}\footnote{The definition of aims and outcomes follows literature for higher education \cite{williamson2011good} and \url{https://www.heacademy.ac.uk/system/files/assessment-learning-outcomes.pdf}.}: 
  Describe the purpose of the skills, but doesn't really include a list of what a practitioner will learn or do. Explaining what a skill is trying to achieve is not the same as saying how it should be done.  
  \item \textbf{Learning outcomes (LOs)}: Defines briefly what practitioners will learn.
  The objectives are statements what prospective learners are able to do. They should clearly describe or define an action bringing about a measurable/quantifiable increase in understanding of that skill.  
 \end{itemize}

On the leaf level, a skill is fine-grained and orthogonal to other skills -- their narrowed scope means they can be taught in sessions ranging from a 1.5 hour lecture up to a 4 hour workshop.
We believe this granularity allows practitioners to cherry-pick the skills relevant to their circumstances, and lecturers and examiners to prepare small lectures with well-defined content.
For technology-dependent skills on the leaf level (e.g., a specific file system or workload manager) the introductory skills are often provided, as they contribute to the foundation of many specialised skills representing a specific hardware or software technology.

The aggregation within the tree is similar to that found in the education circles. Hussey et al.\cite{hussey2008learning} categorised the aggregation of skills into the following levels: individual teaching events, specified for modules or short courses, and those specified for whole degree programmes. 
Although, Hussey et al. conclude that LOs on the coarse grained level are not useful for high-level education, using a similar concept with relaxed level of granularity/abstraction of the learning outcome fits well within the framework of the certification program.  
\kh{den Satz habe ich nicht genau verstanden; als Leser würde ich mir die Kurzbegründung wünschen, die Hussey et al. für ihre Feststellung anführen}
